Dac summary 01/19/2021

### 2021-05-04 final_dac_summary_pull_20210119.Rmd
added stuff for Tim's piece

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830

#### PHQ-2 and PHQ-9 summaries
#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)))) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)))) #n = 261

@@

#looking at just people with phq-2 and 9
phq2_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.2)),] #n=4701
phq9_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.9)),] #n=274

#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76

@@

@@

@@

@@

#vitamin D
hist(data_empi_acc_f_phq$VitD[which(!is.na(data_empi_acc_f_phq$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$FOLATE)))), xlab = "Vitamin D", breaks = 10)

@@

@@

>>>>

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830
print(paste0("Number of unique EMPIS n = ", length(unique(data_empi_acc_f_phq$EMPI)))) #n = 3737

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.2)),] #n=4606

phq9_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

@@

#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))

@@

#phq-2;
print(paste0("N dep + PHQ-2 = ", sum(!is.na(dep_df$PHQ.2)), "; n = ", length(which(dep_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N dep + PHQ-9 = ", sum(!is.na(dep_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(dep_df$PHQ.9 < 5)), "/",
             length(which(dep_df$PHQ.9 >= 5 & dep_df$PHQ.9 < 10)), "/",
             length(which(dep_df$PHQ.9 >= 10 & dep_df$PHQ.9 < 15)), "/",
             length(which(dep_df$PHQ.9 >= 15 & dep_df$PHQ.9 < 20)), "/",
             length(which(dep_df$PHQ.9 >= 20)))) #n = 261

@@

#### ICD 9/10 for Healthy Group
healthy_df <- data_empi_acc_f_phq[(-grep("F3", data_empi_acc_f_phq$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without Depression/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without Depression/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No Depression ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 47

num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10

#### # unique people without dep dx and phq2/9 
dep_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

dep_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

@@

#wbc
hist(data_empi_acc_f_phq$WBC[which(!is.na(data_empi_acc_f_phq$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$WBC)))), xlab = "WBC")

@@

#vitamin D
hist(data_empi_acc_f_phq$VitD[which(!is.na(data_empi_acc_f_phq$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$VitD)))), xlab = "Vitamin D", breaks = 10)

@@

```
```{r frequencies_of_dep_in_phq2_vs_9}
num_dep_phq2 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.2) & (data_empi_acc_f_phq$PHQ.2 >= 3))) #n = 130
num_dep_phq9 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.9) & (data_empi_acc_f_phq$PHQ.9 >= 5))) #n = 184; https://www.sciencedirect.com/science/article/pii/B9780128179338000293 recommends using cut point of 11
num_total_phq2 <-length(which(!is.na(data_empi_acc_f_phq$PHQ.2)))
num_total_phq9 <-length(which(!is.na(data_empi_acc_f_phq$PHQ.9))) 
dep_total_phq_table <- data.frame(matrix(data = c(num_dep_phq2, num_dep_phq9, num_total_phq2, num_total_phq9), nrow = 2, ncol = 2))
names(dep_total_phq_table) <- c("dep", "healthy")
row.names(dep_total_phq_table) <- c("phq2", "phq9")
chisq_dep_phq2_v_phq9 <- chisq.test(dep_total_phq_table)
chisq_dep_phq2_v_phq9
print("observed")
chisq_dep_phq2_v_phq9$observed
print("expected")
chisq_dep_phq2_v_phq9$expected
print("residuals")
chisq_dep_phq2_v_phq9$residuals
```

```{r sex_differences_regressions}

### looking at anyone with phq2s or 9s
males.phq2 <- phq2_subset[which(phq2_subset$SEX == "MALE"),] #n = 951, mean = 0.20
females.phq2 <- phq2_subset[which(phq2_subset$SEX == "FEMALE"),] #n = 3655, mean = 0.26
m_v_f_phq2 <- t.test(males.phq2$PHQ.2, females.phq2$PHQ.2) #p = 0.03 ***

males.phq9 <- phq9_subset[which(phq9_subset$SEX == "MALE"),] #n = 80, mean = 8.63
females.phq9 <- phq9_subset[which(phq9_subset$SEX == "FEMALE"),] #n = 181, mean = 9.13
m_v_f_phq9 <- t.test(males.phq9$PHQ.9, females.phq9$PHQ.9)

#### Looking at depressed group
## interstingly, not the 2:1 ratio we usually see in general world
## phq2 means suggest people are not depressed 
## phq2 means suggest people meet criteria for mild depression

males_dep <- dep_df[(which(dep_df$SEX == "MALE")),] #n = 419/total(4087; 10%) F; mean PHQ2 = 0.61, mean PHQ9 = 13.05
females_dep <- dep_df[(which(dep_df$SEX == "FEMALE")),] #n = 1704/total(12743; 13%)total F; mean = 0.56; mean PHQ9 = 10.61
m_v_f_dep_phq2 <- t.test(males_dep$PHQ.2, females_dep$PHQ.2) #p = 0.66
m_v_f_dep_phq9 <- t.test(males_dep$PHQ.9, females_dep$PHQ.9) #p = 0.24

#chi sq comparing # of pts dx with depression in males vs females; col 1- male dep n, female dep n; col 2- male total n, female total n
### fascinating - only 12% of people even gave a dx of depression in their charts. More likely to have it if female than male; also phq2 mean only slightly higher in females. 
num_dep_m <- dim(males_dep)[1] #n = 419
num_dep_f <-  dim(females_dep)[1]#n = 1704
num_total_m <- length(which(data_empi_acc_f_phq$SEX == "MALE")) #n = 4087
num_total_f <- length(which(data_empi_acc_f_phq$SEX == "FEMALE")) #n = 
m_v_f_table <- data.frame(matrix(data = c(num_dep_m, num_dep_f, num_total_m, num_total_f), nrow = 2, ncol = 2))
names(m_v_f_table) <- c("dep", "total")
row.names(m_v_f_table) <- c("male", "female")
chisq_m_v_f_dist <- chisq.test(m_v_f_table) #p = 4 x 10^-6
chisq_m_v_f_dist
print("observed")
chisq_m_v_f_dist$observed
print("expected")
chisq_m_v_f_dist$expected
print("residuals")
chisq_m_v_f_dist$residuals
#chisq comparing # of

@@

```{r summary_psychosis}
#preprocessing - because these are sent

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830
print(paste0("Number of unique EMPIS n = ", length(unique(data_empi_acc_f_phq$EMPI)))) #n = 3737

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.2)),] #n=4606

phq9_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))

#### ICD 9/10 for Psychosis
psychosis_df <- data_empi_acc_f_phq[grep("F2", data_empi_acc_f_phq$ICD10),] #n = 2123
num_psychosis <- dim(psychosis_df)[1]
unique_empi <- which(unique(data_empi_acc_f_phq$EMPI) %in% data_empi_acc_f_phq$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_psychosis <- length(unique(psychosis_df$EMPI)) #n = 493

print(paste0("N with ICD 9/10 codes for psychosis = ", num_psychosis))

print(paste0("N with ICD 9/10 codes for psychosis and unique EMPI = ", num_unique_EMPI_and_psychosis, " out of ", dim(data_empi_acc_f_phq)[1]))

##### PHQ2 or 9 + ICD 9/10 psychosis
num_phq2_and_psychosis <- length(which(!is.na(psychosis_df$PHQ.2))) #n = 960
print(paste0("N with ICD 9/10 codes for psychosis and phq2 (ALL SCANS) = ", num_phq2_and_psychosis, " out of ", dim(psychosis_df)[1]))

num_phq9_and_psychosis <- length(which(!is.na(psychosis_df$PHQ.9))) #n=140
print(paste0("N with ICD 9/10 codes for psychosis and phq9 (ALL SCANS) = ", num_phq9_and_psychosis, " out of ", dim(psychosis_df)[1]))

#phq-2;
print(paste0("N psychosis + PHQ-2 = ", sum(!is.na(psychosis_df$PHQ.2)), "; n = ", length(which(psychosis_df$PHQ.2 >= 3)), " meeting criteria for psychosis (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N psychosis + PHQ-9 = ", sum(!is.na(psychosis_df$PHQ.9)), "; nopsychosis/mild/mod/mod-severe/severe = ", 
             length(which(psychosis_df$PHQ.9 < 5)), "/",
             length(which(psychosis_df$PHQ.9 >= 5 & psychosis_df$PHQ.9 < 10)), "/",
             length(which(psychosis_df$PHQ.9 >= 10 & psychosis_df$PHQ.9 < 15)), "/",
             length(which(psychosis_df$PHQ.9 >= 15 & psychosis_df$PHQ.9 < 20)), "/",
             length(which(psychosis_df$PHQ.9 >= 20)))) #n = 261

#### # unique people with psychosis dx and phq2/9 -> working on this
psychosis_dx_phq2_unique <- length(unique(psychosis_df$EMPI[!is.na(psychosis_df$PHQ.2)])) #n = 201
print(paste0("N with ICD 9/10 codes for psychosis and phq2 (unique) = ", psychosis_dx_phq2_unique, " out of ", dim(psychosis_df)[1]))

psychosis_dx_phq9_unique <- length(unique(psychosis_df$EMPI[!is.na(psychosis_df$PHQ.9)])) #n = 43
print(paste0("N with ICD 9/10 codes for psychosis and phq9 (unique) = ", psychosis_dx_phq9_unique, " out of ", dim(psychosis_df)[1]))

#### ICD 9/10 for Healthy Group
healthy_df <- data_empi_acc_f_phq[(-grep("F3", data_empi_acc_f_phq$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without psychosis/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without psychosis/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No psychosis ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for psychosis (PHQ2) >= 3")) #n = 47

num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; nopsychosis/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10

#### # unique people without psychosis dx and phq2/9 
psychosis_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq2 (unique) = ", psychosis_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

psychosis_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq9 (unique) = ", psychosis_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

#fcode histos - no one with it at this time. 
#hist(psychosis_df$PHQ.2, main = paste0("PHQ2 and psychosis Histo : n = ", num_phq2_and_psychosis), xlab = paste0("PHQ2"))

#hist(psychosis_df$PHQ.9,main = paste0("PHQ9 and psychosis Histo : n = ", num_phq9_and_psychosis), xlab = paste0("PHQ9"))

#wbc
hist(data_empi_acc_f_phq$WBC[which(!is.na(data_empi_acc_f_phq$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$WBC)))), xlab = "WBC")

#vitamin D
hist(data_empi_acc_f_phq$VitD[which(!is.na(data_empi_acc_f_phq$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$VitD)))), xlab = "Vitamin D", breaks = 10)

```
```{r comparing_out_group_with_Tim_group}
##### checking to see whether we have clinical data for patients who have already been segmented as of 5/4/2021
### had to do some parsing of tim's spreadsheet: /Users/eballer/BBL/msdepression/data/insurance_images_for_depression.csv
### used the following commands to extract the empi and the date -> in tim's they are in the format sub-***** and ses-YYYYMMDD

## more insurance_images_for_depression.csv | cut -f1 -d ','| perl -pe 's/sub-(.*)/$1/' > tim_empi
## more insurance_images_for_depression.csv | cut -f2 -d ','| perl -pe 's/ses-(....)(..)(..)/$2\/$3\/$1/' > tim_dates
## more tim_dates | perl -pe 's/(.*)20(..)/$1$2/' | perl -pe 's/(0)(.)\/(.*)\/(.*)/$2\/$3\/$4/' | perl -pe 's/(.*)\/(0)(.*)\/(.*)/$1\/$3\/$4/' > tim_dates_no_zero_pad

segmented <- read.csv("/Users/eballer/BBL/msdepression/data/insurance_images_for_depression_with_accession.csv", header = F, sep = ",") #n = 4468
names(segmented) <- c("EMPI", "EXAM_DATE", "SES", "ACCESSION_NUM")

#look at the overlap of EMPIs. Won't be able to actually check the matching of scan to person without either accession #s or changing the format of the date. 
number_of_people_in_tims_group_that_are_also_in_mine <- length(which(segmented$ACCESSION_NUM %in% data_empi_acc_f_phq$ACCESSION_NUM)) #2919
overlap_group <- data_empi_acc_f_phq[which(data_empi_acc_f_phq$ACCESSION_NUM %in% segmented$ACCESSION_NUM),]

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- overlap_group[which(!is.na(overlap_group$PHQ.2)),] #n=4606

phq9_subset <- overlap_group[which(!is.na(overlap_group$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(overlap_group$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(overlap_group$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

num_both_phq2_and_9 <- length(which(!is.na(overlap_group$PHQ.2) & !is.na(overlap_group$PHQ.9)))
print(paste0("num people with both phq2 and 9 = ", num_both_phq2_and_9)) #n = 0

#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))

#### ICD 9/10 for Depression
dep_df <- overlap_group[grep("F3", overlap_group$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
unique_empi <- which(unique(overlap_group$EMPI) %in% overlap_group$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493

print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep, " out of ", dim(overlap_group)[1]))

#phq-2;
print(paste0("N dep + PHQ-2 = ", sum(!is.na(dep_df$PHQ.2)), "; n = ", length(which(dep_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N dep + PHQ-9 = ", sum(!is.na(dep_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(dep_df$PHQ.9 < 5)), "/",
             length(which(dep_df$PHQ.9 >= 5 & dep_df$PHQ.9 < 10)), "/",
             length(which(dep_df$PHQ.9 >= 10 & dep_df$PHQ.9 < 15)), "/",
             length(which(dep_df$PHQ.9 >= 15 & dep_df$PHQ.9 < 20)), "/",
             length(which(dep_df$PHQ.9 >= 20)))) #n = 261

#### ICD 9/10 for Healthy Group
healthy_df <- overlap_group[(-grep("F3", overlap_group$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without Depression/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without Depression/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No Depression ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 47

num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10

#### # unique people without dep dx and phq2/9 
dep_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

dep_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

hist(overlap_group$PHQ.2[which(!is.na(overlap_group$PHQ.2))], main = paste0("PHQ-2 Histo : n = ", length(which(!is.na(overlap_group$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(overlap_group$PHQ.9[which(!is.na(overlap_group$PHQ.9))], main = paste0("PHQ-9 Histo : n = ", length(which(!is.na(overlap_group$PHQ.9)))), xlab = "PHQ-9", breaks = 30)

#age histogram
hist(overlap_group$MRI_ENC_AGE[which(!is.na(overlap_group$MRI_ENC_AGE))], main = paste0("Age Histo : n = ", length(which(!is.na(overlap_group$MRI_ENC_AGE)))), xlab = "AGE AT MRI ENCOUNTER")

#tsh
hist(overlap_group$TSH[which(!is.na(overlap_group$TSH))], main = paste0("TSH Histo : n = ", length(which(!is.na(overlap_group$TSH)))), xlab = "TSH")

#hemoglobin
hist(overlap_group$hemoglobin[which(!is.na(overlap_group$hemoglobin))], main = paste0("Hemoglobin Histo : n = ", length(which(!is.na(overlap_group$hemoglobin)))), xlab = "hemoglobin")

#wbc
hist(overlap_group$WBC[which(!is.na(overlap_group$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(overlap_group$WBC)))), xlab = "WBC")

#folate
hist(overlap_group$FOLATE[which(!is.na(overlap_group$FOLATE))], main = paste0("Folate Histo : n = ", length(which(!is.na(overlap_group$FOLATE)))), xlab = "folate", breaks = 10)

#vitamin D
hist(overlap_group$VitD[which(!is.na(overlap_group$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(overlap_group$VitD)))), xlab = "Vitamin D", breaks = 10)

#sex
hist(overlap_group$sex_binarized[which(!is.na(overlap_group$sex_binarized))], 
     main = paste0("Sex Histo : n = ", length(which(!is.na(overlap_group$sex_binarized))), "; M = ", length(which(overlap_group$sex_binarized == 1)), "; F = ", length(which(overlap_group$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

#race
hist(overlap_group$race_binarized[which(!is.na(overlap_group$race_binarized))], 
     main = paste0("Race Histo : n = ", length(which(!is.na(overlap_group$race))), "; White = ", length(which(overlap_group$race_binarized == 1)), "; NW = ", length(which(overlap_group$race_binarized == 2))),
     xlab = "white = 1, other = 2", 
     breaks = 2)
